TITLE by YOUR_NAME_HERE
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# 加载你最终使用的所有组件
# 在这个代码块的分析中。

# 注意，在这个代码块中，将参数 "echo" 设为假。
# This prevents the code from displaying in the knitted HTML output.这可以避免代码混入 HTML 输出显示。
# 应当在文件中，对所有代码块设为 echo=FALSE 。

suppressMessages(library(reshape))
suppressMessages(library(reshape2))
suppressMessages(library(ggplot2))
suppressMessages(library(dplyr))
suppressMessages(library(maps))
suppressMessages(library(RColorBrewer))
suppressMessages(library(GGally))
suppressMessages(library(scales))
suppressMessages(library(memisc))
suppressMessages(library(corrplot))
```

```{r echo=FALSE, Load_the_Data}
# 加载数据

# 1 - fixed acidity: most acids involved with wine or fixed or nonvolatile (do not evaporate readily)
# 2 - volatile acidity: the amount of acetic acid in wine, which at too high of levels can lead to an unpleasant, vinegar taste
# 3 - citric acid: found in small quantities, citric acid can add 'freshness' and flavor to wines
# 4 - residual sugar: the amount of sugar remaining after fermentation stops, it's rare to find wines with less than 1 gram/liter and wines with greater than 45 grams/liter are considered sweet
# 5 - chlorides: the amount of salt in the wine
# 6 - free sulfur dioxide: the free form of SO2 exists in equilibrium between molecular SO2 (as a dissolved gas) and bisulfite ion; it prevents microbial growth and the oxidation of wine
# 7 - total sulfur dioxide: amount of free and bound forms of S02; in low concentrations, SO2 is mostly undetectable in wine, but at free SO2 concentrations over 50 ppm, SO2 becomes evident in the nose and taste of wine
# 8 - density: the density of water is close to that of water depending on the percent alcohol and sugar content
# 9 - pH: describes how acidic or basic a wine is on a scale from 0 (very acidic) to 14 (very basic); most wines are between 3-4 on the pH scale
# 10 - sulphates: a wine additive which can contribute to sulfur dioxide gas (S02) levels, wich acts as an antimicrobial and antioxidant
# 11 - alcohol: the percent alcohol content of the wine
# Output variable (based on sensory data): 
# 12 - quality (score between 0 and 10)
wq <- read.csv('g:\\ku\\udacity_dand_advanced\\Project02_wineQuality\\data\\wineQualityWhites.csv')
str(wq)
summary(wq)
head(wq)
```

# 各变量之间相关性查看1
```{r echo=FALSE, Correlation_Overview_1}
wine_samp <- wine[sample(1:length(wine$quality), 1000),]
ggpairs(wine_samp, wrap_fn_with_param_arg = c(shape = I('.'), outlier.shape = I('.')))
```
# 各变量之间相关性查看2
```{r echo=FALSE, Correlation_Overview_2}
corrplot(cor(wine))
```

# 单变量绘图选择
```{r echo=FALSE, Univariate_Plots}
ggplot(data = wq, aes(x = quality)) +
  geom_histogram(binwidth = 0.5)
```

# 单变量分析

### 你的数据集结构是什么？

### 你的数据集内感兴趣的主要特性有哪些？

### 你认为数据集内哪些其他特征可以帮助你探索兴趣特点？

### 根据数据集内已有变量，你是否创建了任何新变量？

### 在已经探究的特性中，是否存在任何异常分布？你是否对数据进行一些操作，如清洁、调整或改变数据的形式？如果是，你为什么会这样做？



# 双变量绘图选择
```{r echo=FALSE, Bivariate_Plots}
ggplot(data = wq, aes(as.factor(quality), alcohol)) +
  geom_boxplot() +
  xlab("Quality") +
  ylab("Alcohol")

ggplot(data = wq, aes(quality, alcohol)) +
  geom_jitter() +
  geom_smooth(method='lm')

ggplot(data = wq, aes(as.factor(quality), residual.sugar)) +
  geom_boxplot() +
  xlab("Quality") +
  ylab("Residual Sugar") +
  geom_smooth(method='lm')

ggplot(data=data,d aes(as.factor(quality), density))  
+geom_boxplot()+xlab("Quality")+ylab("Density")
ggplot(data=data, aes(quality,density))+geom_jitter()+geom_smooth(method='lm')
```

# 双变量分析

### 探讨你在这部分探究中观察到的一些关系。这些感兴趣的特性与数据集内其他特性有什么区别？

### 你是否观察到主要特性与其他特性之间的有趣关系？

### 你发现最强的关系是什么？




# 多变量绘图选择

```{r echo=FALSE, Multivariate_Plots}

```

# 多变量分析

###  探讨你在这部分探究中观察到的一些关系。通过观察感兴趣的特性，是否存在相互促进的特性？

### 这些特性之间是否存在有趣或惊人的联系呢？

### 选项：你是否创建过数据集的任何模型？讨论你模型的优缺点。

------

# 定稿图与总结

### 绘图一
```{r echo=FALSE, Plot_One}

```

### 描述一


### 绘图二
```{r echo=FALSE, Plot_Two}

```

### 描述二


### 绘图三
```{r echo=FALSE, Plot_Three}

```

### 描述三

------

# 反思